---
title: "Analysis of cell protrusions"
output: html_notebook
---

This notebook collects and summarizes data from skeleton analysis of cell protrusions.

```{r setup}
require(tidyverse)
require(dplyr)

```

The analyze_protrusions.ijm script produces a set of output files, with the following naming conventions:

-   XXX_branch_info.csv

-   XXX_skel_info.csv

where XXX is the base name of the original input file.

All of these files are saved in a single folder.

*Load and merge branch data files

When prompted, select any file within the folder containing the data.

```{r load and merge branch data}

branchSuffix = "_branch_info.csv"
selectedFile <- file.choose()
inputFolder <- dirname(selectedFile) # the input is the parent of the selected file
outputFolder <- dirname(inputFolder) # parent of the input folder

# get file names for branch info
files <- dir(inputFolder, pattern = paste("*",branchSuffix,sep=""))

# tibble is used because of the warning that data_frame is deprecated.
mergedDataWithNames <- tibble(filename = files) %>% # tibble holding file names
  mutate(file_contents =
           map(filename,          # read files into a new data column
               ~ read_csv(file.path(inputFolder, .),
                          locale = locale(encoding = "latin1"),
                          na = c("", "N/A"),
                          show_col_types = FALSE)))

# unnest to make the list into a flat file again,
# but it now has 1 extra column to hold the filename
mergedDataFlat <- unnest(mergedDataWithNames, cols = c(file_contents))

# put the original file base name into a separate column
origfile = str_extract(mergedDataFlat$filename, "[^_]+")

mergedDataFlat <- mergedDataFlat %>%
  mutate(ImageFile = origfile, .before = 1)

# Write an output file of all the merged data ----------

outputFile = paste(basename(inputFolder), "merged", branchSuffix) # spaces will be inserted
write_csv(mergedDataFlat,file.path(outputFolder, outputFile))


```

Calculate the total and median branch length for each image

```{r summarize}
length_total <- mergedDataFlat %>%
  group_by(ImageFile) %>%
  summarize(Total_Length = sum(`Branch length`),
            MedianBranch = median(`Branch length`))

outputFile = paste(basename(inputFolder), "summary", branchSuffix) # spaces will be inserted
write_csv(length_total,file.path(outputFolder, outputFile))

```

